Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-19 draft.tex

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host and field galaxies used in the analysis. Lower: As upper for field galaxies, but shown on a log scale.  The distribution is well described by a Schechter function.}
    \label{fig:mass_hist_hosts_field}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/field_vmax.png}
    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample. The majority of galaxies have no correction, and the distribution of the 1\% that do follows a power-law.
    \label{fig:vmax_field}}
\end{figure}
\subsection{Galaxy properties \label{subsec:properties}}

We estimate global galaxy properties for both the SN host and field galaxy samples by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}. For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES Global Redshift Catalog \citep{Lidman2020}, or more commonly the photometrically derived value. We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF). The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$) and SFR averaged over the proceeding 250 Myr. Upper and lower bounds on physical parameter estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +1$. %To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit. This procedure is repeated 1000 times.

@@

The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1414 SN host galaxies and 48,177 field galaxies.
%%%% INCOMPLETENESS %%%%

@@

\subsection{Supernova hosts \label{subsec:incompletenss_SN_hosts}}
A further limiting factor in the SN host sample is the requirement of a spectroscopic redshift. The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band. The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey. So that we reduce any bias towards SNe in bright hosts that are eCastrillo to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host. This is equivalent to assuming that an efficiency of 0.1 means that for every ten SNe with hosts at that magnitude, only 1 will make it into the sample.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host (green dot-dashed) and field galaxies (orange solid) used in the analysis. Lower: As upper for field galaxies, but shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.2<z<0.5$ (cyan dashes) and $0.5<z<0.75$ (magenta dots).}
    \label{fig:mass_hist_hosts_field}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/field_vmax.png}
    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample. The majority of galaxies have no correction, and the distribution of the 1\% that do follows a power-law.
    \label{fig:vmax_field}}
\end{figure}

@@

The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1414 SN host galaxies and 48,177 field galaxies.

\subsection{Galaxy properties \label{subsec:properties}}

We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}. For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES Global Redshift Catalog \citep{Lidman2020}, or more commonly the photometrically derived value. We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF). The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$). Upper and lower bounds on stellar mass estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +1$.

The results of our SED fitting are shown in Fig. \ref{fig:mass_hist_hosts_field}. The upper panel, with both the SN hosts and field galaxies displayed, shows the vastly different distributions of the two samples. SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$. In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass functions (SMFs) from the ZFOURGE survey \citep{Tomczak2014} that best represent the redshift range of the DES field galaxies. Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMFs, particularly that from $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit. This procedure is repeated 1000 times. 
%%%% INCOMPLETENESS %%%%

@@

\subsection{Supernova hosts \label{subsec:incompletenss_SN_hosts}}
A further limiting factor in the SN host sample is the requirement of a spectroscopic redshift. The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band. The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey. So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host. This is equivalent to assuming that an efficiency of 0.1 means that for every ten SNe with hosts at that magnitude, only 1 will make it into the sample.
